### 2018-03-26 reports/thesis/chapters/5_inference.tex
Stared on empirical null section.

>>>>

By treating each pixel as a hypothesis test, methods for multiple hypothesis can be deployed. At the start of the chapter, a scan from the \texttt{Sep16 120deg} dataset was compared to the \texttt{aRTist} simulation, obtaining a $z$ image.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_image.eps}
        \caption{$z$ image with section highlighted}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo.eps}
        \caption{Histogram of section}
    \end{subfigure}
    }
    \caption{The resulting $z$ image. A histogram of a section of the $z$ image is shown.}
    \label{fig:inference_sub_z}
\end{figure}

A $200\times200$ section of the $z$ image was investigated by plotting the histogram as shown in Figure \ref{fig:inference_sub_z}. One could simply use the BH procedure at the $z_\alpha=2$ level to get the critical region of $\|Z\|>\input{../figures/inference/sub_boundary.txt}$. However a quick look at the histogram will show that almost half of the pixels will be tested as positive. It is questionable whenever such number of positive results is sensible, in particular in an area where defects are not expected.

The histogram showed that the majority of the $z$ statistics are centred around 2 and has a bell shaped curve, a characteristic of the Normal distribution. If the data shows that the majority is centred elsewhere then expected, is it right to then to test the majority of the data as positive? This is an example of model misspecification because it was assumed that the $z$ statistics are distributed as $\normal(0,1)$ when in reality they are distributed as $\normal(\mu_0,\sigma_0^2)$.

The empirical null \citep{efron2004large} adjusts the assumptions made on the $z$ statistics according to the majority of the data and treating it as the norm, relaxing the assumptions needed. It requires the following assumptions: the majority of the data are truly null, non-null test statistics are rare and the null test statistics are Normal distributed.

The method will be described here. Suppose the following test statistics were obtained $z_1,z_2,\dotdotdot,z_n$. First the histogram needs to be smoothed. \cite{efron2004large} recommended using splines but a kernel density estimate \citep{parzen1962on, friedman2001elements} will be used here because it has simpler mathematical properties. The kernel density estimate is
\begin{equation}
	\widehat{p}(z)=
	\frac{1}{nh}
	\sum_{i=1}^n\phi\left(
		\dfrac{z_i-z}{h}
	\right)
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
	h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range. The parameters of the empirical null are estimated using the kernel density estimate. The resulting estimated density is shown in Figure \ref{fig:inference_sub_density_estimate}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_histo_nocritical.eps}
        \caption{Histogram}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/sub_z_parzen.eps}
        \caption{Kernel density estimate}
    \end{subfigure}
    }
    \caption{The density of the test statistics can be estimated using a histogram or a kernel density estimate.}
    \label{fig:inference_sub_density_estimate}
\end{figure}

 Next, the mode of the kernel density estimate, denoted as $\widehat{\mu}_0$. is to be found. This is then used as the mean of the empirical null. The calculation of $\widehat{\mu}_0$ can be numerically using the Newton-Raphson method. Using the mode, the standard deviation of the empirical null is estimated using
 \begin{equation}
 	\widehat{\sigma}_0 = \left[
 		\left.
 			-\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
 		\right|_{z=\widehat{\mu}_0}
 	\right]^{-1/2}
 \end{equation}

\subsection{Statistical Details}

\subsection{Mode Finding}

\subsection{Bandwidth Selection}

\subsection{Results}
